---
title: "eSports Visualizations Descriptive"
author: "Carlos aybar"
output: html_notebook

---

### install tidyverse package
```{r}
install.packages("tidyverse")
```


### load all the necessary libraries
```{r}
library(tidyverse)
library(ggplot2)
```

### importing the data as a csv and viewing the first five rows
```{r}
esport <- read.csv("ESport_Earnings.csv")
head(esport)
```

### creating a boxplot that displays the release year for each game
```{r}
boxplot(esport$Releaseyear,
main = "Distribution of games released every year",
xlab = "Release Year",
ylab = "Count",
col = "blue",
border = "red",
horizontal = TRUE,
ylim = c(1980, 2020),
notch = TRUE
)


```


### subseting the date based on Germany as the top country
### making a histrogram from the new subset with the release year

```{r}
df <- subset(esport, Top_Country == "Germany")

ggplot(data=df, aes(Releaseyear, col = "blue",
fill=Genre)) + 
geom_histogram()+
   labs(title = "Total games released in Germany since 1980 for each Genre",
             subtitle = "Source: Esports Earnings by various Professional Gaming Tournaments" ,
             x = "Release Year",
             y = "Total Games")        
 
```




# Violin Plot to visualize the distribution of games released in the UK since 1980.
```{r}
df <- subset(esport, Top_Country == "United Kingdom")
ggplot(df, aes(x = Top_Country, y = Releaseyear, color = Genre)) + 
  geom_violin(show.legend = TRUE) +
   labs(title = "Total games released in the UK since 1980 for each Genre",
             subtitle = "Source: Esports Earnings by various Professional Gaming Tournaments" ,
             x = "Country",
             y = "Release Year") 
```
